---
title: "Untitled"
author: "Logan"
date: "2/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
Packages <- c("digest", 
              "glue", 
              "reticulate", 
              "knitr",
              "maps",
              "ggplot2",
              "viridis",
              "pals",
              "scico",
              "ggrepel",
              "tidyr",
              "tidyverse",
              "rdrop2",
              "fansi",
              "lubridate",
              "ExcelFunctionsR",
              "gtrendsR"
              )

lapply(Packages, library, character.only = TRUE)
```


```{r}
GoogleFIPS<-read.csv("StateGoogleCrosswalk.csv")
GoogleCross<-read.csv("StateGoogleCrosswalk2.csv")
```

From Google:
Values are calculated on a scale from 0 to 100, where 100 is the location with the most popularity as a fraction of total searches in that location, a value of 50 indicates a location which is half as popular. A value of 0 indicates a location where there was not enough data for this term. Note: A higher value means a higher proportion of all queries, not a higher absolute query count. So a tiny country where 80% of the queries are for "bananas" will get twice the score of a giant country where only 40% of the queries are for "bananas".


#Function Indexed across geography


```{r}
TrendsAcrossGeo<- function(search,time,type,baseline) {

#Index<-gtrends(keyword = search, geo = "US", time = time, gprop =type) #run Google trends for the US given your keyword
#Index<-Index$interest_by_region #pull out interest by state
#Index<-subset(Index, hits==100) #isolate state record with the index =100 
#Index<-merge(Index,GoogleCross, by.x = "location", by.y = "location",all.x = TRUE ) #convert state name to state code
#baseline<-Index$baseline #isolates baseline state code to include in each state-time trend request. 
  #https://stackoverflow.com/questions/20507247/r-repeat-function-until-condition-met

#run API calls in batches keeping a baseline location in each
trendlist <- list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-AL"
,"US-ND"
,"US-AZ"
,"US-AR"
)))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-CA"
,"US-CO"
,"US-CT"
,"US-DE"
))))



trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-DC"
,"US-FL"
,"US-GA"
,"US-HI"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-ID"
,"US-IL"
,"US-IN"
,"US-IA"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-KS"
,"US-KY"
,"US-LA"
,"US-ME"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-MD"
,"US-MA"
,"US-MI"
,"US-MN"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-MS"
,"US-MO"
,"US-MT"
,"US-NE"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-NV"
,"US-NH"
,"US-NJ"
,"US-NM"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-NY"
,"US-NC"
,"US-VT"
,"US-OH"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-OK"
,"US-OR"
,"US-PA"
#,"US-PR"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-RI"
,"US-SC"
,"US-SD"
,"US-TN"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-TX"
,"US-UT"
,"US-VA"
#,"US-VI"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-WA"
,"US-WV"
,"US-WI"
,"US-WY"
))))


trendlist<-c(trendlist,list(gtrends(search, 
                      time = time, 
                      gprop = type,
                      low_search_volume = TRUE,
                      geo = c(baseline   
,"US-AK"
))))

Trends<-rbind(
           trendlist[[1]]$interest_over_time,
           trendlist[[2]]$interest_over_time,
           trendlist[[3]]$interest_over_time,
           trendlist[[4]]$interest_over_time,
           trendlist[[5]]$interest_over_time,
           trendlist[[6]]$interest_over_time,
           trendlist[[7]]$interest_over_time,
           trendlist[[8]]$interest_over_time,
           trendlist[[9]]$interest_over_time,
           trendlist[[10]]$interest_over_time,
           trendlist[[11]]$interest_over_time,
           trendlist[[12]]$interest_over_time,
           trendlist[[13]]$interest_over_time,
           trendlist[[14]]$interest_over_time
            )



Trends<-merge(Trends, GoogleFIPS, by = "geo", all.x = TRUE) #merge fips
Trends$year<-substr(Trends$date, 1,4) #pull out year as separate var
Trends$month<-substr(Trends$date, 6,7) #pull out month as separate var

Trends<-distinct(Trends) #remove repeated baselines


print(Trends)

}




```


###Run Across Geography Queries
```{r}
AcrossState_Weather<-TrendsAcrossGeo(search= "weather",
                                     time="2005-01-01 2017-12-31",
                                     type = "web",
                                     baseline = "US-OR") #start with a best guess based on ranked interest by region https://trends.google.com/trends/explore?date=2005-01-01%202017-12-31&geo=US&q=Weather.

AcrossState_Forecast<-TrendsAcrossGeo(search= "forecast",
                                     time="2005-01-01 2017-12-31",
                                     type = "web",
                                     baseline = "US-AK")

AcrossState_Temperature<-TrendsAcrossGeo(search= "temperature",
                                     time="2005-01-01 2017-12-31",
                                     type = "web",
                                      baseline = "US-MT")

AcrossState_NOAA<-TrendsAcrossGeo(search= "noaa",
                                     time="2005-01-01 2017-12-31",
                                     type = "web",
                                      baseline = "US-FL")

AcrossState_Dogs<-TrendsAcrossGeo(search= "dogs",
                                     time="2005-01-01 2017-12-31",
                                     type = "web",
                                      baseline = "US-ND")


AcrossState_Headache<-TrendsAcrossGeo(search= "headache",
                                     time="2005-01-01 2017-12-31",
                                     type = "web",
                                      baseline = "US-MT")




test<-subset(AcrossState_Weather, AcrossState_Weather$hits==100)#check to see and make sure there isonly one index = 100.
print(test) #If not, select one of the other states on this list and rerun function until only one baseleine exists

test<-subset(AcrossState_Forecast, AcrossState_Forecast$hits==100)
print(test)

test<-subset(AcrossState_Temperature, AcrossState_Temperature$hits==100)
print(test)

test<-subset(AcrossState_NOAA, AcrossState_NOAA$hits==100)
print(test)

test<-subset(AcrossState_Dogs, AcrossState_Dogs$hits==100)
print(test)

test<-subset(AcrossState_Headache, AcrossState_Headache$hits==100)
print(test)


```


###Join "hits" columns from each search and rename accordingly
```{r}
Trends_AcrossState<-left_join(AcrossState_Weather, AcrossState_Forecast[,c("geo","date", "hits")], by = c("geo","date"))%>% #join "hits" columns
      left_join(AcrossState_Temperature[,c("geo","date", "hits")], by = c("geo","date"))%>%
      left_join(AcrossState_NOAA[,c("geo","date", "hits")], by = c("geo","date"))%>%
      left_join(AcrossState_Dogs[,c("geo","date", "hits")], by = c("geo","date"))%>%
      left_join(AcrossState_Headache[,c("geo","date", "hits")], by = c("geo","date"))%>%
      rename(hits_Weather=hits.x, #rename "hits" columns
         hits_Forecast=hits.y,
         hits_Temperature=hits.x.x,
         hits_NOAA=hits.y.y,
         hits_Dogs=hits.x.x.x,
         hits_Headache=hits.y.y.y)%>%
          select(-keyword, #remove unneeded variables
                 -time,
                 -gprop,
                 -catagory)




```


#Function Indexed within each geography
```{r}
TrendsWithinGeo<-function(search, time, type ){
state <- select(GoogleCross, baseline) #Make FD of only state names
state.list <- setNames(split(state, seq(nrow(state))), rownames(baseline)) # make each state a single item in a list
state.list <- lapply(state.list, paste, collapse = " ") #convert to text strings (to work with Gtrend function)

State_index<-gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[1]])$interest_over_time
              State_index<-rbind(State_index, gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[2]])$interest_over_time)
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[3]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[4]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[5]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[6]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[7]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[8]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[9]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[10]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[11]])$interest_over_time)
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[12]])$interest_over_time)   
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[13]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[14]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[15]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[16]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[17]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[18]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[19]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[20]])$interest_over_time)
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[21]])$interest_over_time)
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[22]])$interest_over_time)   
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[23]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[24]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[25]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[26]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[27]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[28]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[29]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[30]])$interest_over_time)
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[31]])$interest_over_time)
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[32]])$interest_over_time)   
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[33]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[34]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[35]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[36]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[37]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[38]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[39]])$interest_over_time) 
              #State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[40]])$interest_over_time) #exclude PR
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[41]])$interest_over_time)
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[42]])$interest_over_time)   
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[43]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[44]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[45]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[46]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[47]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[48]])$interest_over_time) 
              #State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[49]])$interest_over_time) #exclude VI
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[50]])$interest_over_time)
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[51]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[52]])$interest_over_time) 
              State_index<-rbind(State_index,gtrends(search, time = time,  gprop = type,low_search_volume = TRUE, geo = state.list[[53]])$interest_over_time) 
              
              
State_index<-merge(State_index, GoogleFIPS, by = "geo", all.x = TRUE) #merge fips
State_index$year<-substr(State_index$date, 1,4) #pull out year as separate var
State_index$month<-substr(State_index$date, 6,7) #pull out month as separate var  

print(State_index)
              
}            

```


#Run within State Trends
```{r}
#Set Parameters
search<-"weather"
time<-"2005-01-01 2017-12-31"
type<-"web"

Within_StateWeather<-WithinStateTrend(search, time, type)

```



```{r}
WithinState_Weather<-TrendsWithinGeo(search= "weather",
                                     time="2005-01-01 2017-12-31",
                                     type = "web")

WithinState_Forecast<-TrendsWithinGeo(search= "forecast",
                                     time="2005-01-01 2017-12-31",
                                     type = "web")

WithinState_Temperature<-TrendsWithinGeo(search= "temperature",
                                     time="2005-01-01 2017-12-31",
                                     type = "web")

WithinState_NOAA<-TrendsWithinGeo(search= "noaa",
                                     time="2005-01-01 2017-12-31",
                                     type = "web")

WithinState_Dogs<-TrendsWithinGeo(search= "dogs",
                                     time="2005-01-01 2017-12-31",
                                     type = "web")


WithinState_Headache<-TrendsWithinGeo(search= "headache",
                                     time="2005-01-01 2017-12-31",
                                     type = "web")




```


###Join "hits columns from each search and rename accordingly
```{r}
Trends_WithinState<-left_join(WithinState_Weather, WithinState_Forecast[,c("geo","date", "hits")], by = c("geo","date"))%>%
      left_join(WithinState_Temperature[,c("geo","date", "hits")], by = c("geo","date"))%>%
      left_join(WithinState_NOAA[,c("geo","date", "hits")], by = c("geo","date"))%>%
      left_join(WithinState_Dogs[,c("geo","date", "hits")], by = c("geo","date"))%>%
      left_join(WithinState_Headache[,c("geo","date", "hits")], by = c("geo","date"))%>%
      rename(hits_Weather=hits.x,
         hits_Forecast=hits.y,
         hits_Temperature=hits.x.x,
         hits_NOAA=hits.y.y,
         hits_Dogs=hits.x.x.x,
         hits_Headache=hits.y.y.y)
```



#Plots and Figures
```{r, fig.width=20,fig.height=8}

#Individual search volume within state
ggplot(subset(Trends_WithinState, geo==c("US-AZ" )), aes(x = date, y = hits_Forecast)) + 
  geom_line(aes(color = geo))

ggplot(subset(Trends_WithinState, geo==c("US-AK")), aes(x = date, y = hits_Forecast)) + 
  geom_line(aes(color = geo))+
  scale_colour_manual(values = c('blue','red'))


#Search volume across states where AK=100
ggplot(subset(Trends_AcrossState, geo==c("US-AK","US-AZ" )), aes(x = date, y = hits_Forecast)) + 
  geom_line(aes(color = geo))+
  scale_colour_manual(values = c('blue','red'))

```


#Export Data
```{r}
write.csv(Trends_AcrossState,"Trends_AcrossState.csv")
write.csv(Trends_WithinState,"Trends_WithinState.csv")


```



